\documentclass[11pt,a4paper]{article}

% ---------- Packages ----------
\usepackage[left=0.70in,right=0.70in,top=0.50in,bottom=0.50in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ---------- Section formatting ----------
% Use \section (not \section*) so titleformat applies properly
\titleformat{\section}
  {\vspace{2pt}\large\bfseries\uppercase}
  {}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing*{\section}{0pt}{7pt}{5pt}

% ---------- List spacing ----------
\setlist[itemize]{leftmargin=1.5em, itemsep=1pt, topsep=2pt, parsep=0pt, partopsep=0pt}

% ---------- Helpers ----------
\newcommand{\roleline}[2]{\textbf{#1} \hfill {\small\textit{#2}}}

\newcommand{\eduspace}{\vspace{3pt}}

\newcommand{\eduentry}[3]{%
  \textbf{#1}\hfill \textbf{#2}\\
  \textit{#3}\par
}

\begin{document}

% ================= HEADER =================
\begin{center}
  {\Huge \textbf{Rajat Nimje}}\\[4pt]
  {\large Data Analyst \ $|$ \ B.Tech Computer Engineer $|$ Vinoba Bhave Nagar, Nagpur}\\[6pt]
  
  \href{mailto:rajatnimje434@gmail.com}{rajatnimje434@gmail.com} \;$|$\;
  +91 9049478926 \;$|$\;
  \href{https://www.linkedin.com/in/connect-with-rajat-nimje/}{LinkedIn} \;$|$\;
  \href{https://github.com/rajat2003fg}{GitHub} \;$|$\;
  \href{https://rajat2003fg.github.io/Portfolio/}{Portfolio}
\end{center}

\vspace{2pt}

% ================= SUMMARY =================
\section{Summary}
Proficient Data Analyst and B.Tech (Computer Engineering) graduate with strong fundamentals in
\textbf{SQL, Excel, Power BI, and Python}.
Experienced in \textbf{data cleaning, EDA, KPI reporting, and visualization} using Pandas and Matplotlib
to produce actionable insights. Seeking an \textbf{entry-level Data Analyst / BI Analyst} opportunity.

% ================= SKILLS =================
\section{Skills}
\begin{tabularx}{\textwidth}{@{}l X@{}}
\textbf{Analytics \& BI:}  & SQL, Excel (Pivot Tables, VLOOKUP/XLOOKUP), Power BI, Tableau \\[2pt]
\textbf{Python:}           & Pandas, NumPy, Matplotlib (EDA, data cleaning, aggregation) \\[2pt]
\textbf{Tools:}            & Git, GitHub, n8n \\[2pt]
\textbf{Web (basic):}      & HTML, CSS \\
\end{tabularx}

% ================= PROJECTS =================
\section{Projects}

\roleline{E-Commerce Customer Behavior \& Shopping Trends Analysis}{Python, Pandas, Matplotlib}
\begin{itemize}
  \item Analyzed \textbf{3,900+ transactions} to identify revenue drivers, seasonal trends, and high-value categories.
  \item Built segmentation views to compare spend patterns across demographics using pivot-style summaries.
  \item Created box plots and distribution charts to highlight outliers and product/category variance.
  \item Summarized insights into clear, decision-focused observations for stakeholder reporting.
\end{itemize}

\vspace{2pt}
\roleline{Statistical Profiling of Global Book Sales}{Python, Pandas, Matplotlib}
\begin{itemize}
  \item Cleaned and standardized records by handling nulls and anomalies using vectorized Pandas operations.
  \item Performed multi-stage aggregations to rank publisher performance and analyze unit-sales distributions.
  \item Visualized trends and long-tail behavior using charts that highlight top contributors and outliers.
  \item Structured outputs into reusable tables suitable for BI dashboard integration.
\end{itemize}

\vspace{2pt}
\roleline{AI-Powered WhatsApp Automation for Restaurant Order Management}{n8n, Gemini LLM}
\begin{itemize}
  \item Built a no-code WhatsApp chatbot workflow to automate order placement and handle customer FAQs.
  \item Designed conversation flows, intent routing, and automated responses to reduce manual handling.
  \item Focused on consistent customer experience and faster query resolution through automation.
\end{itemize}

% ================= EDUCATION =================
\section{Education}
\eduentry{B.Tech in Computer Engineering}{2021 -- 2025}{Smt. Radhikatai Pandav College of Engineering, Nagpur}
\eduspace
\eduentry{Higher Secondary Education (Class XII)}{2020 -- 2021}{Shri Ramswami Junior College, Nagpur}
\eduspace
\eduentry{Secondary Education (Class X)}{2018 -- 2019}{New English High School, Nagpur}

% ================= CERTIFICATIONS =================
\section{Certifications}
\begin{itemize}
  \item \textbf{Cloud Computing} --- NPTEL (2025)
\end{itemize}

% ================= ADDITIONAL =================
\section{Additional}
\begin{tabularx}{\textwidth}{@{}l X@{}}
\textbf{Languages:} & Hindi, English, Marathi \\[2pt]
\textbf{Hobbies:}   & Bike riding, trekking \\
\end{tabularx}

\end{document}